---
title: "Replication of Hoffmann et al. (2020)"
author: "Jack Murphy"
date: "05/05/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(readxl)
library(meta)
library(metafor)
library(lfe)
library(lme4)
library(stargazer)
library(ggpubr)
library(jtools)
library(RColorBrewer) 
library(rgeos)
library(rnaturalearth)
```

```{r}
setwd("~/Desktop/Gov52/rep_project/meta-article")

countrydata <- read_xlsx("../data/Environmental Change and Migration_Country Level Data.xlsx")

all_data <- get(load("../data/Environmental Change and Migration_Meta and Country Data.RData"))

world <- ne_countries(returnclass = "sf")

## MODELS IN MAIN TEXT

# Baseline controls
con_base <- c("interaction", "fe_time", "fe_spatial", "control_sum") 

# Environmental variables 1
con_clim1 <- c("pre_var", "rapidonset", "tem_lev", "tem_var")

# Environmental variables 2
con_clim2 <- c("env_lag_dum", "env_timespan_dum", "env_other_dum")

# Migration variables
con_mig <- c("internal", "dest_low", "dest_high", "dest_ambi") # , 

# Compositional measures 1: Regional composition
con_context1 <- "nonoecd"

# Compositional measures 2: Composition by country characteristics
con_context2 <-c("L", "LM", "UM", "agr", "conflict_mepv_5")

## MODELS IN SUPPLEMENTARY MATERIALS

# control variables used in models
con_control <- c("income_channel", "conflict_channel", "controls_political", "controls_population", "controls_pastmigr", "controls_econlevel", "controls_culture", "controls_geo")

# Sample size of models
con_samplesize <- c("countrysample", "yearscovered")

# Time and spatial fixed effects
con_fixedeffects <- c("fe_time", "fe_spatial")

# Weighting and further estimation features
con_estimation <- c("weights", "lin", "robustness_check")

# Publication characteristics of studies
con_pub1 <- c( "published1")

# Additional controls for focus on differential time periods
con_time2 <- c("period_start" , "period_end")


#prop.table(table(meta$temperature));  table(meta$temperature)
#prop.table(table(meta$precipitation)); table(meta$precipitation)
#prop.table(table(meta$rapidonset)); table(meta$rapidonset)
#prop.table(table(meta$internal)); table(meta$internal)

# Defining data and weights
dat <- meta
wt <- 1/meta$stanse^2

```

```{r}

## 
## FUNCTIONS TO IMPLEMENT MODELS *****************************
##  

func.felm <- function(yname,xnames, fixedeffect.cluster) {
  controls <- paste(xnames, collapse = "+")
  fe.c <- paste(fixedeffect.cluster,  collapse = "|" )
  formula <- as.formula(paste(yname,"~",controls, "|", fe.c, sep = ""))
  return(formula)
}

func.lmer <- function(yname,xnames) {
  controls <- paste(xnames, collapse = "+")
  formula <- as.formula(paste(yname,"~",controls,"+(1|paper)", sep = ""))
  return(formula)
}

```


## Overview of the Original Paper

"A meta-analysis of country-level studies on environmental change and migration"
by Roman Hoffmann, Anna Dimitrova, Raya Muttarak, Jesus Crespo Cuaresma, and 
Jonas Peisker, published in Nature in October 2020, conducted, as the
title suggests, a meta-analysis of 30 selected studies published between 2006
and 2019 examining environmental change and out-migration.[^note_call] The authors 
extracted estimates of the relationship between environmental change factors and
migration from these 30 papers, generating 1803 such estimates each of which became
a separate observation in their own models. 

The authors focus on country-level studies that consider a variety of environmental
factors like changing temperatures, heavy storms, and droughts. They standardized
the effects of these factors by finding the mean and standard deviation
for effects used across multiple studies, and expressing those values in terms of
standard deviations from their respective means. 

The authors then review the studies generally, categorizing the environmental 
changes researched into rapid-onset or gradual changes, noting that a large 
majority of the used estimates were for gradual environmental changes rather 
than rapid-onset events such as floods or landslides. They note that 88.0% of the
estimates focus on international migration, and that 27 of the studies find a 
notable positive relationship between environmental changes and migration.

After weighting the study results for their precision, the paper finds a 
statistically significant positive relationship between such
environmental changes and migration, though the strength and direction of the 
relationship vary between studies. The authors found that "on average, a one 
standard deviation change in the environmental conditions leads to an increase in 
migration by 0.021 standard deviations." 

Their first figure explores the heterogeneity of the studies analysed: regressing
characteristics of the models the original studies used. They found that 
rapid-onset changes in the environment have large
impacts on migration, as do rainfall anomalies (like droughts), but changes
in temperatures by contrast have a small - yet statistically significant - impact.
Unfortunately the publicly available code did not include the lines needed
to replicate this figure, so it is not included here.

The below table is the first table included in the paper, the replicated
results completely match the original published results. It displays the 
resulting estimates for the impact of increasing numbers of variables
on migration, as calculated by five increasingly complex fixed-effect
linear models.

The first model shows the estimated impact of temperature-level changes
on migration in terms of standard deviations of migration, relative to
a comparable change in precipitation levels.

The model presented in the second column takes into account broader timeframes
for the relationship between environmental changes and migration, looking at
5- and 10-year timeframes as opposed to 1-year time frames examined in the 
first column.

The third model estimates take into account both these extended time frames as
well as global migration flows. However as most of the original studies did not 
measure internal migration, the differences are small (albeit robust).

The fourth and fifth models dive into the international migration flows, finding larger
effects tying environmental changes to migration towards non-OECD and low- or 
middle-income countries. The difference between the internal and global migration 
effects and these effects corroborates findings in the literature "that environmental
migration is often short-distance, regional and temporary."

These last two models take various samples of the countries examined in the original
studies, sorting them into groups such as non-OECD, low-income, low-middle-income,
upper-middle-income, and agriculturally dependent countries. This grouping is 
intended to evaluate the difference in impact of environmental changes
on migration depending on the economic characteristics of the country of origin. 
These estimates indicate that the economic constraints faced by residents of
low-income countries restrict migration following environmental changes as
contrasted with the movements of residents of higher-income countries.

[^note_call]: The data and code used in this replication report can be obtained 
at ##insert github link here ##

```{r results = 'asis'}

## 
## TABLE 1 WEIGHTED FELM MODEL: STANDARDIZED COEFF AS OUTCOME -----------------
## 

## COLUMN 1
m1a <- func.felm("stancoeff", c(con_base, con_clim1),
                 c("paper", "0", "paper"))
m1b <- felm(m1a , data = dat, weights=wt)
# summary(m1b)

## COLUMN 2
m2a <- func.felm("stancoeff", c(con_base, con_clim1, con_clim2), 
                 c("paper", "0", "paper"))
m2b <- felm(m2a , data = dat, weights=wt)
# summary(m2b)

## COLUMN 3
m3a <- func.felm("stancoeff", c(con_base, con_clim1, con_clim2, con_mig), 
                 c("paper", "0", "paper"))
m3b <- felm(m3a , data = dat, weights=wt)
# summary(m3b)

## COLUMN 4
m4a <- func.felm("stancoeff", c(con_base, con_clim1, con_clim2, con_mig, con_context1), 
                 c("paper", "0" , "paper"))
m4b <- felm(m4a , data = dat, weights=wt) 
# summary(m4b) 

## COLUMN 5
m5a <- func.felm("stancoeff", c(con_base,  con_clim1, con_clim2, con_mig, con_context2), 
                 c("paper", "0" , "paper"))
m5b <- felm(m5a ,  data = dat, weights=wt)
# summary(m5b)


## TABLE 1
stargazer(m1b, m2b, m3b, m4b, m5b,
          type="latex",
          out="../figures/table 1_baseline_m1-m5.doc",
          ci=F, 
          notes="Test",
          model.names = T,
          single.row = T,
          font.size = "small",
          omit = c("interaction", "fe_time", "fe_spatial", "control_sum", 
                   "yearscovered", "countrysample"),
          header = FALSE)

rm(m1a, m2a, m3a, m4a, m5a, m1b, m2b, m3b, m4b, m5b)

```


\newpage

In extending this paper I would amend three figures, although as the figures
themselves do convey information adequately, the proposed extensions are more
aesthetic than substantive.

The first is figure 2, which visualizes the distribution of the effects of
give types of environmental hazards on migration using violin plots. The
original is replicated below.

```{r}
##
## FIGURE 2 - VIOLIN PLOTS: DISTRIBUTION OF ENVIRONMENTAL EFFECTS BY ENVIRONMENTAL HAZARD -----
## 


meta %>% 
  mutate(
    climate_rec = as.factor(
      ifelse(rapidonset == 1,"Rapid-onset disaster",
             ifelse(pre_lev ==1, "Precipitation level change",
                    ifelse(pre_var == 1,"Precipitation variability / anomaly",
                           ifelse(tem_lev == 1, "Temperature level change",
                                  ifelse(tem_var == 1, 
                                         "Temperature variability / anomaly",
                                         "NA")))))),
    climate_rec = fct_reorder(.f = climate_rec, .x = stancoeff.w, 
                              .fun = median, na.rm = TRUE, .desc = TRUE)
  ) %>% 
  ggplot(aes(y = climate_rec, x = stancoeff.w)) + 
  geom_vline(xintercept = 0) +
  geom_jitter(width = 0.3, size = 0.7, alpha = 0.3) +
  geom_violin(scale="width", bw = 0.5, fill = NA) + 
  geom_boxplot(outlier.shape=NA, width=0.32, fill="grey", alpha=0.5, 
               position = position_dodge2(preserve = "single"))+
  labs(
    y = "",
    x = "Precision-weighted standardized environmental effect"
  ) +
  coord_cartesian(xlim = c(-5,7)) +
  scale_x_continuous(breaks = seq(-5,7, 1))+
  theme(axis.text.y=element_text(size=10))

ggsave("../figures/figure 2_violin_differences in environmental effects by hazards.jpg", 
       dpi=600, width=8, height=6)
```

The proposed extension to this figure would make it more visually intuitive,
adding varying point shapes which highlight the outliers of the graph, and
colors that 

```{r}
##
## FIGURE 2 - Extension -----
## 


meta %>% 
  mutate(
    climate_rec = as.factor(
      ifelse(rapidonset == 1,"Rapid-onset disaster",
             ifelse(pre_lev ==1, "Precipitation level change",
                    ifelse(pre_var == 1,"Precipitation variability / anomaly",
                           ifelse(tem_lev == 1, "Temperature level change",
                                  ifelse(tem_var == 1, 
                                         "Temperature variability / anomaly",
                                         "NA")))))),
    climate_rec = fct_reorder(.f = climate_rec, .x = stancoeff.w, 
                              .fun = median, na.rm = TRUE, .desc = TRUE)
  ) %>% 
  ggplot(aes(y = climate_rec, x = stancoeff.w)) + 
  geom_vline(xintercept = 0) +
  geom_jitter(width = 0.3, size = 0.7, alpha = 0.3, color = "darkgoldenrod1") +
  geom_violin(scale="width", bw = 0.5, fill = NA) + 
  geom_boxplot(outlier.shape=NA, width=0.32, fill="grey", alpha=0.5, 
               outlier.color = "brown1",
               position = position_dodge2(preserve = "single"))+
  labs(
    y = "",
    x = "Precision-weighted standardized environmental effect"
  ) +
  coord_cartesian(xlim = c(-5,7)) +
  scale_x_continuous(breaks = seq(-5,7, 1))+
  theme(axis.text.y=element_text(size=10))

ggsave("../figures/figure 2_violin_differences in environmental effects by hazards_extended.jpg", 
       dpi=600, width=8, height=6)

```

The second would be figure 3, similarly adding color to the plotted data and
regression lines to make the visualisations more appealing.

The original visualisations are made below:

```{r}
##
## FIGURE 3 - LINE PLOTS: PREDICTED ENVIRONMENTAL EFFECTS BY SAMPLE COMPOSITION -----
## 

## Estimating predicted values using a mixed random effects model

pred1a <- func.lmer("stancoeff", c(con_base, con_context2)) # including only compositional shares
pred1b <- lmer(pred1a, data = dat , weights=wt)
# summary(pred1b)


pred1b_coef <- coefficients(pred1b)

dat.predict <- dat %>% 
  mutate(predict = mean(pred1b_coef$paper$`(Intercept)`)+
           mean(pred1b_coef$paper$fe_time)+ # predictions based on coefficients for models controling for time ...
           mean(pred1b_coef$paper$fe_spatial)+ # ... and spatial fixed effects
           L*mean(pred1b_coef$paper$L)+
           LM*mean(pred1b_coef$paper$LM)+
           UM*mean(pred1b_coef$paper$UM)+
           agr*mean(pred1b_coef$paper$agr)+
           conflict_mepv_5*mean(pred1b_coef$paper$conflict_mepv_5))

# summary(dat.predict$predict)


## Plotting predicted effect sizes
plot1 <- dat.predict %>% 
  filter(agr<0.5 & conflict_mepv_5<0.5) %>% 
  ggplot(aes(y=predict, x=M))+
  geom_hline(yintercept = 0) +
  geom_jitter(width=0.05, height=0.01, alpha=0.25)+
  geom_smooth(method="lm", color = "black", formula = y ~ x) +
  labs(
    x = "% middle-income countries in sample", 
    y = "Predicted environmental effect"
    ) +
  coord_cartesian(
    ylim = c(-0.05, 0.05), 
    xlim = c(0, 1)
    )+
  scale_y_continuous(breaks = seq(-0.05,0.05,0.025))+
  scale_x_continuous(labels=scales::percent)+
  theme(axis.title=element_text(size=13.8),
        axis.text=element_text(size=11.3))
#plot1

plot2 <- dat.predict %>%
  filter(L>0.8) %>% 
  ggplot(aes(y=predict, x=agr))+
  geom_hline(yintercept = 0) +
  geom_jitter(width=0.03, height=0.01, alpha=0.25)+
  geom_smooth(method="lm",se=T, color="Black", formula = y ~ x)+
  labs(
    x = "% agriculturally dependent countries in sample",
    y = ""
    )+
  coord_cartesian(
    ylim = c(-0.05, 0.05), 
    xlim = c(0, 1)
    )+
  scale_y_continuous(breaks = seq(-0.05,0.05,0.025))+
  scale_x_continuous(labels=scales::percent)+
  theme(axis.title=element_text(size=13.3),
        axis.text=element_text(size=11.3))
# plot2

plot3 <- dat.predict %>%
  filter(agr<0.5) %>% 
  ggplot(aes(y=predict, x=conflict_mepv_5))+
  geom_hline(yintercept = 0) +
  geom_jitter(width=0.03, height=0.01, alpha=0.25)+
  geom_smooth(method="lm", color="black", formula = y ~ x)+
  labs(
    x = "% conflict countries in sample",
    y = ""
    ) +
  coord_cartesian(
    ylim = c(-0.05, 0.05), 
    xlim = c(0, 1)
    ) +
  scale_y_continuous(breaks=seq(-0.05,0.05,0.025))+
  scale_x_continuous(labels=scales::percent)+
  theme(axis.title=element_text(size=13.8),
        axis.text=element_text(size=11.3))

 # plot3

plot123 <- ggarrange(plot1, plot2, plot3, align="h", nrow = 1, labels = "auto")

plot1
plot2
plot3

#plot123 

ggsave("../figures/figure 3_line plots_sample composition effects.jpg", width=15, height=5, dpi=600)

rm(pred1a,pred1b, plot1,plot2,plot3,plot123)
```

The proposed amended plots would look something like this:

```{r}
##
## FIGURE 3 - LINE PLOTS: Extension -----
## 

## Estimating predicted values using a mixed random effects model

pred1a <- func.lmer("stancoeff", c(con_base, con_context2)) # including only compositional shares
pred1b <- lmer(pred1a, data = dat , weights=wt)
# summary(pred1b)


pred1b_coef <- coefficients(pred1b)

dat.predict <- dat %>% 
  mutate(predict = mean(pred1b_coef$paper$`(Intercept)`)+
           
           # predictions based on coefficients for models controling for time ...
           
           mean(pred1b_coef$paper$fe_time)+ 
           
           # ... and spatial fixed effects
           
           mean(pred1b_coef$paper$fe_spatial)+ 
           L*mean(pred1b_coef$paper$L)+
           LM*mean(pred1b_coef$paper$LM)+
           UM*mean(pred1b_coef$paper$UM)+
           agr*mean(pred1b_coef$paper$agr)+
           conflict_mepv_5*mean(pred1b_coef$paper$conflict_mepv_5))

# summary(dat.predict$predict)


## Plotting predicted effect sizes

plot1 <- dat.predict %>% 
  filter(agr<0.5 & conflict_mepv_5<0.5) %>% 
  ggplot(aes(y=predict, x=M))+
  geom_hline(yintercept = 0) +
  geom_jitter(width=0.05, height=0.01, alpha=0.25, color = "azure2")+
  geom_smooth(method="lm", color = "black", formula = y ~ x) +
  labs(
    x = "% middle-income countries in sample", 
    y = "Predicted environmental effect"
    ) +
  coord_cartesian(
    ylim = c(-0.05, 0.05), 
    xlim = c(0, 1)
    )+
  scale_y_continuous(breaks = seq(-0.05,0.05,0.025))+
  scale_x_continuous(labels=scales::percent)+
  theme(axis.title=element_text(size=13.8),
        axis.text=element_text(size=11.3))
# plot1

plot2 <- dat.predict %>%
  filter(L>0.8) %>% 
  ggplot(aes(y=predict, x=agr))+
  geom_hline(yintercept = 0) +
  geom_jitter(width=0.03, height=0.01, alpha=0.25, color = "bisque1")+
  geom_smooth(method="lm",se=T, color="Black", formula = y ~ x)+
  labs(
    x = "% agriculturally dependent countries in sample",
    y = ""
    )+
  coord_cartesian(
    ylim = c(-0.05, 0.05), 
    xlim = c(0, 1)
    )+
  scale_y_continuous(breaks = seq(-0.05,0.05,0.025))+
  scale_x_continuous(labels=scales::percent)+
  theme(axis.title=element_text(size=13.3),
        axis.text=element_text(size=11.3))
# plot2

plot3 <- dat.predict %>%
  filter(agr<0.5) %>% 
  ggplot(aes(y=predict, x=conflict_mepv_5))+
  geom_hline(yintercept = 0) +
  geom_jitter(width=0.03, height=0.01, alpha=0.25, color = "darkseagreen")+
  geom_smooth(method="lm", color="black", formula = y ~ x)+
  labs(
    x = "% conflict countries in sample",
    y = ""
    ) +
  coord_cartesian(
    ylim = c(-0.05, 0.05), 
    xlim = c(0, 1)
    ) +
  scale_y_continuous(breaks=seq(-0.05,0.05,0.025))+
  scale_x_continuous(labels=scales::percent)+
  theme(axis.title=element_text(size=13.8),
        axis.text=element_text(size=11.3))

  # plot3

plot123 <- ggarrange(plot1, plot2, plot3, align="h", nrow = 1, labels = "auto")

plot1
plot2
plot3

#plot123    
ggsave("../figures/figure 3_line plots_sample composition effects_extended.jpg", 
       width=15, height=5, dpi=600)

rm(pred1a,pred1b, plot1,plot2,plot3,plot123)


```


The last would be figure 4,
which color-codes the countries of the world according to their predicted migration
based on their historical exposure to environmental change from 1960 to 2000.
This data is measured in standard deviations of the world distribution and their 
economic and sociopolitical characteristics measured in the year 2000. The latter 
is measured using income level, agricultural dependency, and conflict as in model
5 from Table 1. 

```{r}
##
## FIGURE 4 - MAP: PREDICTED ENVIRONMENTAL EFFECT ON MIGRATION WORLDWIDE ------
## 

countrydata <- 
  countrydata %>%   
  mutate(
    predictedresponse = 
      mean(pred1b_coef$paper$`(Intercept)`)+
      
   # predictions based on coefficients for models controling for time ...

      mean(pred1b_coef$paper$fe_time)+ 
     
   #... and spatial fixed effects
     
      mean(pred1b_coef$paper$fe_spatial)+ 
      L*mean(pred1b_coef$paper$L)+
      LM*mean(pred1b_coef$paper$LM)+
      UM*mean(pred1b_coef$paper$UM)+
      agr*mean(pred1b_coef$paper$agr),
    conflict_mepv_5*mean(pred1b_coef$paper$conflict_mepv_5),
    predictedmig = env_change*predictedresponse,
    predictedmig_cat = cut(predictedmig, breaks = c(-Inf,-0.025,0.025,0.05,0.1,0.15,0.2,Inf))
  )

# summary(countrydata$predictedmig)

map_world <- 
  world %>% 
  mutate(adm0_a3 = recode(adm0_a3, "SDS"="SSD")) %>% 
  right_join(countrydata, by = c("adm0_a3" = "iso3c"))

map_world %>% 
  ggplot() +
    geom_sf(aes(fill = predictedmig_cat)) + 
    coord_sf(crs = "+proj=eqearth") + 
    theme_minimal() +
    theme(
      axis.text = element_blank(),
    ) +
    scale_fill_manual(
      name = "Predicted migration", 
      values = c(
        "(-Inf,-0.025]" = "#3f7ad9",
        "(-0.025,0.025]" = "#dee4fa",
        "(0.025,0.05]"="#fae0de",
        "(0.05,0.1]"="#de9999",
        "(0.1,0.15]"="#db6969",
        "(0.15,0.2]"="#de4949",
        "(0.2, Inf]"="#db1414"
      ),
      labels = c(
        "negative [-0.55,-0.025]",
        "none (-0.025,0.025]",
        "very low (0.025,0.05]",
        "low (0.05,0.1]",
        "moderate (0.1,0.15]",
        "high (0.15, 0.20]",
        "very high (0.2, 0.50]"),
      na.translate = FALSE
    )
ggsave("../figures/figure 4_map_predicted environmental migration.jpg", width = 10, 
       height=4.5, dpi=600)

```


My proposed extension to this figure would be converting this map which identifies
hotspots of environmental migration based on data from 2000 into an animation
that displays global out-migration trends over a longer time period. 
More than half of the studies incorporated in this meta-analysis contain data 
from years after 2000, with 16 of the 30 total studies including data up to 2010. 
In addition, half of the studies included data from before 1975. However, only
4 studies of the 30 had data from both prior to 1975 and later than 2000. 

The selected country-level data, in terms of income-status identification for
each country, whether the country was involved in a conflict, and whether a country 
is more of an agricultural exporter or importer, and their environmental
change score in a particular year, could be calculated for any year. 

An animated progression through the years based on the available data for
each country in each year would be a fascinating extension of this project, providing not
only an understanding of what regions' migration patterns are being affected by 
environmental changes and how, but also of how those patterns are developing
year by year. This information is currently not conveyed by the original 
visualisation.

Unfortunately, the original authors of the paper did not include the data
used to construct their countrydata dataframe (which is the 2000 snapshot). 
However, with the same data used to build that dataframe, similar ones could 
certainly be built for other years and allow for a time-lapse animation using
the same mapping functions as well as a package like gganimate.

## Conclusion

To replicate this project I consulted the code and data provided by the original
authors at https://doi.org/10.7910/DVN/HYRXVV. I am grateful to the original
authors for making this data and code publicly available.

Their data was well-organised and accessible, and their variables used in the
model were correctly coded. The code provided ran easily with the specified 
packages and reproduced practically identical results, with very minor 
variations due to the chosen sampling method. The first figure I was unable
to replicate, as the authors did not publish its code. However, the remaining
tables and figures were replicable and thus I have high confidence that the
first figure's data and code are reliable. 

The authors created vectors of several combinations of key variables to 
plug into the custom functions func.felm and func.lmer that they created. The 
models used in the main section of the paper were all run using the func.felm
function, producing fixed-effect linear models. 

The results make sense: based on the data provided by the authors, the 
environmental changes, and in particular rapid-onset events, increase
out-migration from the affected countries. This is corroborated elsewhere 
in literature not included in this meta-analysis, such as in:

Gori Maia, Alexandre, and Schons, Stella Zucchetti. "The Effect of Environmental 
Change on Out-migration in the Brazilian Amazon Rainforest." Population and 
Environment 42, no. 2 (2020): 183-218.

and 

De Lellis, Pietro, Ruiz Marín, Manuel, and Porfiri, Maurizio. "Modeling Human 
Migration Under Environmental Change: A Case Study of the Effect of Sea Level 
Rise in Bangladesh." Earth's Future 9, no. 4 (2021): N/a.

To extend the original models I recommend creating an animated version of figure 
4, a world map showing migration hot spots predicted based on factors including
conflict, GDP per capita, and environmental changes. Such a map, if animated
as a time-lapse, would provide a further dimension to understand the implications
of the findings of this meta-analysis.

I also produced a sixth linear model using the variables 
examined in the authors' fifth with the addition of regional factor variables
to identify how the same results varied from one region to another. The results
of this model are below.

```{r results = 'asis'}

regions <- c("ssa", "europena", "asia", "lac", 
                                "mena")

# "mig_destination", "region"

m6a <- func.felm("stancoeff", c(con_base,  con_clim1, con_clim2, con_mig,
                                con_context2, "region"), 
                 c("paper", "0" , "paper"))
m6b <- felm(m6a,  data = dat, weights=wt)


summary(m6b)

stargazer(m6b,
          type="latex",
          # out="table 1_baseline_m1-m5.doc",
          ci=T, 
          notes="Test",
          model.names = T,
          single.row = T,
          font.size = "regular",
          omit = c("interaction", "fe_time", "fe_spatial", "control_sum", 
                   "yearscovered", "countrysample"),
          header = FALSE)
```



\newpage
# Bibliography

De Lellis, Pietro, Ruiz Marín, Manuel, and Porfiri, Maurizio. "Modeling Human 
Migration Under Environmental Change: A Case Study of the Effect of Sea Level 
Rise in Bangladesh." Earth's Future 9, no. 4 (2021): N/a.

Gori Maia, Alexandre, and Schons, Stella Zucchetti. "The Effect of Environmental 
Change on Out-migration in the Brazilian Amazon Rainforest." Population and 
Environment 42, no. 2 (2020): 183-218.

Hoffmann, Roman, Dimitrova, Anna, Muttarak, Raya, Crespo Cuaresma, Jesus, and Peisker, Jonas. "A Meta-analysis of Country-level Studies on Environmental Change and Migration." Nature Climate Change 10, no. 10 (2020): 904.

Meager, Rachel, "Understanding the Average Impact of Microcredit Expansions: A Bayesian Hierarchical Analysis of Seven Randomized Experiments"  The American Economic Journal: Applied Economics, January 2019.

```{r}

```




